Toxic code snippets on Stack Overflow

### 2017-10-19 cloverflow-tse/cloverflow.tex
Finalise the draft to be ready for Jens to look at.

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
% We studied online code clones on the popular programming Q\&A
% website, Stack Overflow, and their issues on outdated code and
% software licensing violations. 
\FIXME{Outdated.~Revise the last.}~Online code clones are code fragments that are copied from software
projects or online sources to Stack Overflow as examples in
questions and answers.
% They can be discovered by using code clone
% detectors, yet they are inherently different from normal code clones
% in software projects in several aspects. 
Due to an absence of a checking mechanism after the code has been
copied to Stack Overflow, online code clones may suffer from
becoming outdated or violating the original software license.
% Moreover, we also found that majority of online code clones do not
% contain the license of their originals.
We present a study incorporating several state-of-the-art tools and
techniques to automatically extract, prioritise, and filter detected
online clone pairs between 144,064 Java code snippets on Stack
Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 32,533 non-trivial online clone
candidates. Our investigation of 3,636 manually confirmed clone
pairs revealed strong evidence that 112 clones have been copied from
a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
to be outdated and potentially harmful for reuse.  Furthermore, we
found 357 code snippets on Stack Overflow that violate the license
of their original software.
% These snippets are questionable for reuse.
% Our study is among the first to address the problem of
% outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

Our survey of Stack Overflow answerers shows that online code cloning occurs on
Stack Overflow. Stack Overflow answerers frequently
clone code from other locations, such as their personal projects, company
projects, and open source projects, to Stack Overflow as a solution or
a complement to a solution. The code cloning activity on Stack Overflow
is obviously beneficial considered the popularity of Stack Overflow and its
influence on software development~\FIXME{find citations}. On the other hand,
there is also a downside caused by low quality, defective, and harmful code
snippets that are reused without an awareness by millions of users.

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2014-11-21) */
public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
  try {                                                 try {
    buffer.reset(b1,s1,l1); /* parse key1 */              buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                              key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */              buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                              key2.readFields(buffer);
  } catch (IOException e) {                               $$@buffer.reset(null,0,0); /* clean up reference */@
    throw new RuntimeException(e);                      } catch (IOException e) {
  }                                                       throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */         }
}                                                       return compare(key1, key2); /* compare them */
                                                      }
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{WritableComparator.java}}. The one from the
		Stack Overflow post 22315734 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). Its Apache v.2.0 license is also missing.}
	\label{fig:before-after}
\end{figure*}

@@

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in January 2016.
% The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information of posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006},
we empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode} methods,
which are not interesting for the study.
Each snippet was extracted from the dump and saved to a file. Moreover, we
filtered out irrelevant code snippets that were part of the accepted answers
but were not written in Java by using regular expressions and manual checking.
~\FIXME{@Jens, should I mention I use PMD CPD to help here? More confusing?}.
Finally we obtained
72,365 Java code snippets containing 1,840,581 lines\footnote{Measured by cloc:
	\url{https://github.com/AlDanial/cloc}} of Java source code. The median size of the
snippet is 17 lines.

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared and 607 (26\%)
conflicts were discussed and resolved. There are 145 conflicts caused by
one investigator being more careful than the other and able to find evidence of 
copying while the other could not. They result in a better classification,
 i.e.~from UD to QS or EX. 
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples in questions and answers. % They
Due to an absence of a checking mechanism after the code has been copied to
Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
being outdated or violating the original software license. We present a study
incorporating several state-of-the-art tools and techniques to automatically
extract and filter detected online clone pairs between 72,365 Java code snippets
on Stack Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
Our investigation of the online clone pairs revealed strong evidence that 154
clones have been copied from a Qualitas project to Stack Overflow.  We found 101
of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
we found 214 code snippets on Stack Overflow that violate the license of their
original software. We surveyed 201 high-reputation Stack Overflow answerers
(33\% response rate) and found that 69 of them have never been notified of
outdated code in the answers and 26 of them rarely or never fix the outdated
code. Only 3 answerers explicitly include software license in their answers and
138 answerers never check for licensing conflicts between their copied code
snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

@@

Our survey of Stack Overflow answerers shows that online code cloning occurs on
Stack Overflow. Stack Overflow answerers frequently
clone code from other locations, such as their personal projects, company
projects, and open source projects, to Stack Overflow as a solution or
a complement to a solution. The code cloning activity on Stack Overflow
is obviously beneficial considered the popularity of Stack Overflow and its
influence on software development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
there is also a downside caused by low quality, defective, and harmful code
snippets that are reused without an awareness by millions of users.

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2014-11-21) */
public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
  try {                                                 try {
    buffer.reset(b1,s1,l1); /* parse key1 */              buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                              key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */              buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                              key2.readFields(buffer);
  } catch (IOException e) {                               $$@buffer.reset(null,0,0); /* clean up reference */@
    throw new RuntimeException(e);                      } catch (IOException e) {
  }                                                       throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */         }
}                                                       return compare(key1, key2); /* compare them */
                                                      }
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{WritableComparator.java}}. The one from the
		Stack Overflow post 22315734 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). Its Apache v.2.0 license is also missing.~\FIXME{@Jens Could you please make the underline clearer?}}
	\label{fig:before-after}
\end{figure*}

@@

\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. % The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information of posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
methods, which are not interesting for the study. Each snippet was extracted
from the dump and saved to a file. Moreover, we filtered out irrelevant code
snippets that were part of the accepted answers but were not written in Java by
using regular expressions and manual checking. ~\FIXME{@Jens, should I mention I
	use PMD CPD to help filtering SO code snippets here? Will it be too confusing?}.
Finally we obtained 72,365 Java code snippets containing 1,840,581
lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
source code. The median size of the snippet is 17 lines.

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared and 607 (26\%)
conflicts were discussed and resolved. There are 145 conflicts caused by
one investigator being more careful than the other and able to find evidence of 
copying while the other could not. They result in a better classification,
 i.e.~from UD to QS or EX.~\FIXME{@Jens Is it better to just report \% of conflicts
 between TP vs.~FP classifications (e.g. only from QS, SQ, EX, UD, BP, IN <--> AC)?
Because 26\% does not come from a wrong validation, it's mostly just a different classification.}
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.
